---
title: "Rightwatching Data Report"
author: "Rightwatching"
date: !r Sys.Date()
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



## Überblick

### `r input$barchart_header1`

`r input$barchart_text1`

```{r barchart, fig.width=12}
make_barchart(data = chronik_filtered(), level = input$barchart_option1)
```


### `r input$county_timline_header1`

`r input$county_timline_text1`

```{r county_timline, fig.width=12}
validate(
        need(input$county_timeline_option1, 'Bitte mindestens einen Landkreis aussuchen!')
      )
      make_county_timeline(data = chronik_by_county(), selected_kreise = input$county_timeline_option1) 
```

## Daten im Kontext


### `r input$context_map_header1`
`r input$context_map_text1`
```{r contextmap1, fig.width=12}
make_context_map1(party = input$context_map_option2)
```


### `r input$context_map_header2`
`r input$context_map_text2`
```{r contextmap2, fig.width=12}
make_context_map2()
```


### `r input$context_map_header3`
`r input$context_map_text3`
```{r contextmap3, fig.width=12}
make_context_map3()
```


### `r input$context_map_header4`
`r input$context_map_text4`
```{r contextmap4, fig.width=12}
make_context_map4()
```


## Daten prüfen


### `r input$source_multiple_header1`
`r input$source_multiple_text1`
```{r source multiple map, fig.width=12}
make_source_multiple_map()
```


### `r input$source_map_header1`
`r input$source_map_text1`
```{r source map, fig.width=12}
make_source_map()
```




